---
title: "index.Rmd"
author: "Xiaotong(Katherine) Zhang, Yenmy Vo, Natalie Hinds, Kasper Li"
date: "November 14, 2022"
output:
  pdf_document: default
  word_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("tidyr")
library("knitr")
library("dplyr")
source("https://raw.githubusercontent.com/kkkatherine323/project-itsyenmyvo22/main/source/summary_information.R")
source("https://raw.githubusercontent.com/kkkatherine323/project-itsyenmyvo22/main/data/Gun_Table.R")
source("https://raw.githubusercontent.com/kkkatherine323/project-itsyenmyvo22/main/data/poverty_nkilled_graph.R")
```


# **Gun Violence in the US: Project Proposal**


## Code Name: waterguns

## _Authors:_
**Natalie Hinds (Nhinds2@uw.edu)
 Kasper Li(jiaxul9@uw.edu)
 Katherine Zhang (Xiaotz7@uw.edu)
 Yenmy Vo (yenmyvo@uw.edu)**

### INFO-201: Technical Foundations of Informatics - The Information School - University of Washington

November 2022

## Summary Information

```{r, echo=FALSE, message = F, include=FALSE}
info <- summary_info
info$deaths_sales_18
info$deaths_sales_21
info$max_deaths_state
info$highest_rate_state
info$highest_deaths_one_day
```

We use datasets that are specific to incidents of gun violence, such as the state where the violence occurred, the date it occurred, how many casualties there were, how many areas sold guns to 18+, how many areas sold guns to 21+, and local poverty rates. The dataset we chose includes U.S. gun violence incidents from 2013 to 2018. To demonstrate the main purpose of what our project is studying, we chose to calculate five variables through the dataset that are representative of our research questions. These are the states in the dataset with the highest number of deaths due to gun violence, the states with the highest poverty rates, the highest number of deaths in a day, the number of deaths in areas where guns are sold to people over 18 years old, and the number of deaths in areas where guns are sold to people over 21 years old. The results obtained were `r info$deaths_sales_18` deaths in areas where guns were sold to people over the age of 18 and `r info$deaths_sales_21` deaths in areas where guns were sold to people over the age of 21. The data set showed `r info$highest_deaths_one_day` gun violence deaths in a day, and the state with the highest number of deaths due to gun violence was `r info$max_deaths_state`. In addition, the state with the highest poverty rate was `r info$highest_rate_state`.


### Summary Table


* This file will eventually become your project report for **P02: Exploratory Data Analysis**. Specifically, you will write rmarkdown to report your exploratory data analysis.

```{r pressure, echo=FALSE}
all_sum_df
```


## ACCESSING THE /source DIRECTORY
### Example 1: Source some code and run a function
```{r}
# Example 1: Note relative path, which can be read: Up one
# directory(..), down into source (/source), and
# then "source" an R file (data_access.R)
source("../source/data_access.R")
data_access_test()
```

### Example 2: Initialize a variable and then use it
```{r}
# Example 1: This function was "sourced" above
msg <- data_access_test(" Morgan!")
```

> `r msg` Hope you have a good day!!


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
